Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-09-19 review_article.Rmd

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(g1), 0, .5, 0.5, 0.5) +
  draw_plot(rasterGrob(g2), 0.5, 0.5, 0.5, 0.5) +
  draw_plot(rasterGrob(g3), 0.0, 0.0, 0.5, 0.5) +
  draw_plot(rasterGrob(g4), 0.5, 0, 0.5, 0.5)+
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 15)
```

Table: \label{tab:usa} Maps used to present statistics for the Uited States of America

>>>>

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(g1), 0, .5, 0.5, 0.5) +
  draw_plot(rasterGrob(g2), 0.5, 0.5, 0.5, 0.5) +
  draw_plot(rasterGrob(g3), 0.0, 0.0, 0.5, 0.5) +
  draw_plot(rasterGrob(g4), 0.5, 0, 0.5, 0.5)+
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 15) +
  theme_set(theme_cowplot())
```

Table: \label{tab:usa} Maps used to present statistics for the United States of America
